Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-19 paper/ijcai/paper.tex
comment
update to this year's template
some issues fixed

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
\usepackage{ijcai18}
% The file ijcai18.sty is the style file for IJCAI-18 (same as ijcai08.sty).

@@

\begin{abstract}
Several approaches have been proposed to improve automated softaware fault
diagnosis, aiming to reduce the effort and costs spent in debugging. This
paper reports the outcome of a study
performed to reassess\Rui{dismistify? We need to say something on why we
decided to mistify this combination...} the impact of combining Dynamic Slicing (DS) with
spectrum-based fault localization (SFL), a technique we coin as Tandem-FL. We
suspect that several highly suspiscious components \Rui{I am using components to be
more generic} --- often involved in failing, but seldom in passed executions ---
may be unrelated to the bug. Thus, we use Mozilla's Lithium engine to minimize
the failing tests source files that comprise the highest scored faulty
statements from the Defects4j dataset\Rui{not clear why this is in here for
the reader: Mozilla, minimizing test cases, ... }. The impact of Tandem-FL is evaluated
through computing the SFL score \Rui{SFL score: a reader does not know what that is}
of each fault before and after minimization\Rui{minimization: unknown to the
reader... He thinks that the study is on slicing}.
This study also discusses on limitations of dynamic slicing, such as the potential
of missing faulty statements. Our
results show that adding combining SFL with dynamic slicing improves the diagnostic
accuracy in \Rui{x\% on average}, hence leading to the root cause of oberved failures faster.
\end{abstract}

@@

Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and Spectrum-Based Fault Localization
(\sfl{}) are two very popular techniques that leverage different principles
to automate fault isolation. An example of a MBSD is Dynamic
Slicing~\cite{Agrawal:1990:DPS:93542.93576}
as well as some work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927},
a technique that traces back statements in the code that influence some point of interest, such as the evaluation
of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
does not analyze code. Instead, it is a black-box, statistical fault
localization method that computes suspiciousness values associated
with program entities (e.g., methods) based on coverage information gathered
during the execution of test cases as well as the
output of test cases. More precisely, \sfl{} uses coverage information
of passing and failing test cases to identify likely faulty
statements and produces on output a list of program entities ranked in
decreasing order of suspiciousness.
\ds{} and \sfl{} are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{}
ranks the relevant parts of the code.

>>>>

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
\usepackage{ijcai19}
% The file ijcai18.sty is the style file for IJCAI-18 (same as ijcai08.sty).

@@

\begin{abstract}
Several approaches have been proposed to improve automated software fault
diagnosis, aiming to reduce the effort and costs spent in debugging. This
paper reports the outcome of a study
performed to dismistify\Rui{We need to say something on why we
decided to mistify this combination...} the impact of combining Dynamic Slicing (DS) with
spectrum-based fault localization (SFL), a technique we coin as Tandem-FL. We
suspect that several highly suspiscious components --- often involved in failing, 
but seldom in passed executions ---
may be unrelated to the bug. Thus, we use Mozilla's Lithium engine to minimize
the failing tests source files that comprise the highest scored faulty
statements from the Defects4j dataset\Rui{not clear why this is in here for
the reader: Mozilla, minimizing test cases, ... }. The impact of Tandem-FL is evaluated
through computing the SFL score \Rui{SFL score: a reader does not know what that is}
of each fault before and after minimization\Rui{minimization: unknown to the
reader... He thinks that the study is on slicing}.
This study also discusses on limitations of dynamic slicing, such as the potential
of missing faulty statements. Our
results show that combining SFL with dynamic slicing improves the diagnostic
accuracy in \Rui{x\% on average}, hence leading to the root cause of observed failures faster.
\end{abstract}

@@

Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and Spectrum-Based Fault Localization
(\sfl{}) are two very popular techniques that leverage different principles
to automate fault isolation. An example of a MBSD is Dynamic
Slicing~\cite{Agrawal:1990:DPS:93542.93576}
as well as some work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927},
a technique that traces back statements in the code that influence some point of interest, such as the evaluation
of a failing assertion. In contrast to \ds{} \Rui{DS, not introduced at this point
in the intro}, \sfl{}~\cite{7390282}
does not analyze code. Instead, it is a black-box, statistical fault
localization method that computes suspiciousness values associated
with program entities (e.g., methods) based on coverage information gathered
during the execution of test cases as well as the
output of test cases. More precisely, \sfl{} uses coverage information
of passing and failing test cases to identify likely faulty
statements and produces on output a list of program entities ranked in
decreasing order of suspiciousness.
\ds{} and \sfl{} are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{}
ranks the relevant parts of the code.
